\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-10-27 reviews/response.Rmd

> "Would it be possible to have a plot for each day in a calendar plot with thick lines separating the months?  That kind of plot is common for calendar heatmaps."  I think that is important.  Perhaps they can build it in.  If not, why not?

The white space between months already emphasises the separations between months. The lines separating the months are also thicker than the ones separating the days in the calendar plot. These sit in the background to make the data plot more visible, which follows the Tufte's rules.

> The paper describes a display based on months.  Months have different lengths and are not comparable.  The paper says that a mixture of different plots is best.  A list of possible plots with pros and cons would be helpful.  Which features can be seen in one plot, which in another?

Many data plots is recommended by Unwin (), to form a comprehensive picture about the data during the EDA process. It is distracting for the main message of this paper to make a list of possible plots with pros and cons. However, our paper shows traditional displays in Figure 2, 3, and 11 as possible plots, and the captions describe the main features that we can read from the plots. The calendar display is not to replace but to complement them, and this should be apparent from the captions and text associated with the full suite of plots.

### 2019-10-28 reviews/response.Rmd

> Page 17, figure 10. I don't see negative correlation. Just two slopes, both positive. Am I missing something?

We deleted the sentence, "This is due to the morning and afternoon commuter patterns in Figure 6: the adjacent hours are positively correlated when approaching to the peak hour but negatively correlated when moving away from the peak.", to mitigate the confusion.

> Page 19, first sentence. The meaning of this is not clear. Rephrase.

Done. We rephrased "As a data restructuring tool" to "The previous calendar plots are static, made with **ggplot2**."

@@

We've reduced the size of panel labels to give more room to the data display. Time labels are now made to show 6 and 18 to avoid confusion.

The colour scheme is suggested by reviewer 3 before, which is colour-blind and grey-scale print friendly.

> Page 23. Suggest dropping figure 13. Or move to supplementary material.

We dropped the boxplots as in figure 13, and the associated paragraph.

@@

Done.

# Reviewer 1 {-}

> "Would it be possible to have a plot for each day in a calendar plot with thick lines separating the months?  That kind of plot is common for calendar heatmaps."  I think that is important.  Perhaps they can build it in.  If not, why not?

The white space between months already emphasises the separations between months. The lines separating the months are also thicker than the ones separating the days in the calendar plot. These sit in the background to make the data plot more visible.

@@

> The paper describes a display based on months.  Months have different lengths and are not comparable.  The paper says that a mixture of different plots is best.  A list of possible plots with pros and cons would be helpful.  Which features can be seen in one plot, which in another?

Many data plots is recommended by Unwin & Valero-Mora (2018), to form a comprehensive picture about the data during the EDA process. It is distracting for the main message of this paper to make a list of possible plots with pros and cons. However, our paper shows traditional displays in Figure 2, 3, and 11 as possible plots, and the captions describe the main features that we can read from the plots. The calendar display is not to replace but to complement them, and this should be apparent from the captions and text associated with the full suite of plots.

@@

> p22 "with noticeable variations on Thursdays" based on only 26 data points is over-interpretation.

It's half-hourly data, meaning 26 Thursdays * 48 per day = 1248 data points. But we dropped the boxplot as in figure 13 including this sentence.

> p22 "The other two households (1 and 4) tend to consume more energy with more variation on the weekends relative to the week days, reflecting work and leisure patterns."  The vertical scaling makes it very difficult to see this.  Inspecting the data with individual scales offers some support but not a lot.

We dropped the boxplot as in figure 13, and the associated paragraph including this sentence.

### 2019-10-28 calendar-vis.Rmd
proofread

authors:
- name: Earo Wang
  affiliation: Department of Econometrics and Business Statistics, Monash University
  email: earo.wang@monash.edu

- name: Dianne Cook
  affiliation: Department of Econometrics and Business Statistics, Monash University

- name: Rob J Hyndman
  affiliation: Department of Econometrics and Business Statistics, Monash University

@@

* $k = 1, \dots , 7$ is the day of the week, that is the first day of the month.
* $d = 28, 29, 30$ or $31$ representing the number of days in any month.
* $(i, j)$ is the grid position where $1 \le i \le 5$, is the row (week within the month), $1 \le j \le 7$, is the column (day of the week), with $(1, 1)$ being in the upper left corner.
* $g = k, \dots,(k + d - 1)$ indexes the day in the month, inside the 35 possible cells.

>>>>

authors:
- name: Earo Wang
  affiliation: Monash University & CSIRO Data61
  email: earo.wang@monash.edu

- name: Dianne Cook
  affiliation: Monash University

- name: Rob J Hyndman
  affiliation: Monash University

@@

* $k = 1, \dots , 7$ is the day of the week, that is the first day of the month.
* $d = 28, 29, 30$ or $31$ representing the number of days in any month.
* $(i, j)$ is the grid position, where $1 \le i \le 5$ is the row (week of the month), and $1 \le j \le 7$ is the column (day of the week), with $(1, 1)$ being in the upper left corner.
* $g = k, \dots,(k + d - 1)$ indexes the day in the month, inside the 35 possible cells.

### 2019-10-28 calendar-vis.tex
proofread

  \author{
        Earo Wang \\
    Department of Econometrics and Business Statistics, Monash University\\
     and \\     Dianne Cook \\
    Department of Econometrics and Business Statistics, Monash University\\
     and \\     Rob J Hyndman \\
    Department of Econometrics and Business Statistics, Monash University\\
      }
  \maketitle
} \fi

@@

\begin{itemize}
\tightlist
\item
  \(k = 1, \dots , 7\) is the day of the week, that is the first day of the month.
\item
  \(d = 28, 29, 30\) or \(31\) representing the number of days in any month.
\item
  \((i, j)\) is the grid position where \(1 \le i \le 5\), is the row (week within the month), \(1 \le j \le 7\), is the column (day of the week), with \((1, 1)\) being in the upper left corner.
\item
  \(g = k, \dots,(k + d - 1)\) indexes the day in the month, inside the 35 possible cells.
\end{itemize}

>>>>

  \author{
        Earo Wang \\
    Monash University \& CSIRO Data61\\
     and \\     Dianne Cook \\
    Monash University\\
     and \\     Rob J Hyndman \\
    Monash University\\
      }
  \maketitle
} \fi

@@

\begin{itemize}
\tightlist
\item
  \(k = 1, \dots , 7\) is the day of the week, that is the first day of the month.
\item
  \(d = 28, 29, 30\) or \(31\) representing the number of days in any month.
\item
  \((i, j)\) is the grid position, where \(1 \le i \le 5\) is the row (week of the month), and \(1 \le j \le 7\) is the column (day of the week), with \((1, 1)\) being in the upper left corner.
\item
  \(g = k, \dots,(k + d - 1)\) indexes the day in the month, inside the 35 possible cells.
\end{itemize}
